\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{tgpagella}
\usepackage{geometry}
\geometry{
  letterpaper,
  left=20mm,
  %right=
  %bottom=
  top=15mm}
\pagestyle{empty}
\usepackage{fontawesome5}

\newlength{\iconwidth}
\setlength{\iconwidth}{1.2em}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}

\definecolor{lavender}{HTML}{8E7CC3}
\definecolor{darklavender}{HTML}{674EA7}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=darklavender]{hyperref}

\usepackage{titlesec}

\titleformat{\section}
  {\color{darklavender}\Large}
  {}{0em}{}[{\color{darklavender}\titlerule[1pt]}]

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

\newcommand{\work}[4]{
\noindent  \textbf{#1}
\hfill
\mbox{
    \parbox{10em}{%
    \centering\textbf{#2}}} \par
\noindent \textit{#3} \par
\vspace*{0.5em}
\noindent\hangindent=2em\hangafter=0 \small #4
\normalsize \par}

\newcommand{\skill}[2]{
\noindent\hangindent=2em\hangafter=0
\parbox{3\spacebox}{
\textsc{#1}}
#2 \par
\vspace{0.5em}
}

\newcommand{\lan}[2]{
\noindent\hangindent=2em\hangafter=0
\parbox{\spacebox}{%
    \textbf{#1}}
    #2 \par}

\newcommand{\education}[4]{
\noindent  \textbf{#1}
    \hfill
    \mbox{
        \parbox{10em}{%
        \centering\textbf{#2}}} \par
    \noindent \textit{#3} \par
    \vspace*{0.5em}
    \noindent\hangindent=2em\hangafter=0 \small #4
\normalsize \par}

\begin{document}
\thispagestyle{empty}
\noindent
\textbf{\Huge \textcolor{darklavender}{Marco Antonio} \textcolor{lavender}{Sandoval Espinosa}}\par

\begin{flushleft}

\end{flushleft}\par

\noindent
\begin{itemize}[itemsep=0em]
\item[\faAt] \href{mailto:mrsandv@pm.me}{mrsandv@pm.me}
\item[\faLinkedin]\href{https://linkedin.com/in/mrsan}{linkedin.com/in/mrsan}
\item[\faPhone] \href{tel:+525580367317}{+52 55 803 673 17}
\item[\faMapMarker] \textcolor{darklavender}{Mexico City.}
\end{itemize}

\section*{Tech Skills}
\skill{Programming languages}{\textsc{JavaScript},  \textsc{TypeScript},  \textsc{Golang} }
\skill{Frameworks}{\textsc{ReactJS, NextJS, Gatsby, Express, Echo}}
\skill{Frontend}{\textsc{HTML, CSS, SCSS, Tailwind, MUI}}
\skill{Databases}{\textsc{MongoDB, Redis, PostgreSQL, MariaDB}}
\skill{Cloud}{\textsc{AWS, Digital Ocean, GCP, Vercel, Azure}}
\skill{Tools}{\textsc{Markdown, Git, Docker, Podman, \LaTeX}}
\skill{ }{\textsc{Bash, Jasper Reports, IA agents}}

\section*{Experience}
\work{Web team lead}{Jan 2020 -- Jul 2025}{Flink/Webull MX}{
\begin{itemize}[leftmargin=*, itemsep=0em, label=- ]
    \item Standardized and structured NextJS and TypeScript as core stack across web projects for the business.
    \item Led the migration of legacy systems to a modern stack and pipelines for existing and new projects.
    \item Designed high-performance web solutions, focused on optimizing development processes and improving user experience(UX).
    \item Implemented CI/CD pipelines using GitLab CI, AWS ECS/ECR, Lambdas, and containers, which streamlined development and maintenance processes in production.
    \item Designed and implemented APIs for company projects, modeling schemas and optimizing queries for transactional databases.
    \item Established code standards and best practices, creating documentation and configuration guidelines to ensure code quality and consistency.
    \item Managed projects using agile methodologies, ensuring on-time delivery and achievement of objectives.
    \item Gathered and analyzed internal projects requirements, design workflows, mockups and required functionality to achieve each project goal.
\end{itemize}
}
\vspace*{1em}
\work{Frontend developer}{Nov 2018 -- Jan 2020}{Forward company}{
\begin{itemize}[leftmargin=*, itemsep=0em, label=-]
    \item Tasked with improving the UI of the company's Learning Management System(LMS) by migrating 100\% of the inline styles to SCSS files, improving maintainability and scalability.
    \item Implemented dynamic HTML content delivery, using configuration and localization files for a fully customized user experience.
    \item Collaborated with stakeholders to gather and refine the LMS platform requirements, designing UX flows, mockups, and functionalities to address user needs and implement new features.
    \item Led development and maintenance of main web frontend components, ensuring stability and performance of the platform with modern and legacy browsers, including mobile devices.
\end{itemize}}
\vspace*{1em}
\work{Technology Consultant}{Nov 2018 -- Ene 2020}{Spanish Training Academy}{
\begin{itemize}[leftmargin=*, itemsep=0em, label=-]
    \item Developed an informative website in WordPress hosted on a Linux Ubuntu server, managing courses information, prices, contact forms and essential pages to promote the academy's offerings.
    \item Implemented and configured a Moodle LMS platform on a DigitalOcean server
    \item Implemented SSL certificates, maintaned platform databases and oversaw user management for the platform teachers to enable seamless and secure teaching courses.
    \item Provided IT support and managed GSuite tools to ensure smooth operations and improve productivity within the organization.
\end{itemize}}

\section*{Education}
\education{Physics BS.}{2009 -- 2015}{UNAM}{}
\education{Software and Network Design Engineer}{2023 -- present}{UVM}{}

\section*{Languages}
\lan{Spanish}{Native}
\lan{English}{B2}

\section*{Interests}
\begin{itemize}[leftmargin=*, itemsep=0em, label=-]
    \item Computer science
    \item Finances
    \item Education
    \item Video games
\end{itemize}

\end{document}
